---
title: "Project 2"
author: "Paul Hwang"
date: "2023-04-17"
output: html_document
---


```{r}
library(data.table)
library(dplyr)
library(DataExplorer)
```


## Load Data Publica

    id: post id number on facebook
    html: HTML of the ad as collected by the Political Ad Collector
    political: number of Political Ad Collector users who have voted that the ad is political
    not_political: number of Political Ad Collector users who have voted that the ad is not political
    title: ad title
    message: ad content
    thumbnail: link for a thumbnail of the profile image (of the advertiser)
    created_at: date ad was first collected by the Political Ad Collector
    updated_at: the most recent time that it got an impression OR the most recent time it was voted on
    lang: language of the ad. always en-US.
    images: link for images included in the ad
    impressions: number of times the ad has been seen by the Political Ad Collector
    political_probability: calculated by the classifier. data only includes ads with a probability >=0.7
    targeting: Facebook’s “Why am I seeing this?” disclosure provided to Political Ad Collector users
    suppressed: value is false. suppressed ads are excluded from this data set because they were misclassified.
    targets: a parsed version of targeting
    advertiser: the account that posted the ad
    entities: named entities mentioned in the ad, extracted using software
    page: the page that posted the ad
    lower_page: the Facebook URL of the advertiser that posted the ad (the “page” column, lowercased)
    targetings: an array of one or more of Facebook’s “Why am I seeing this?” disclosures provided to Political Ad Collector users
    paid_for_by: for political ads, the entity listed in Facebook’s required disclosure as having paid for the ad
    targetedness: an internal metric for estimating how granularly an ad is targeted, used for sorting in the ProPublica search interface

```{r}
publica <- fread("/Users/paulhwang/Desktop/Distributed Computing/Project 2/Data/fbpac-ads-en-US.csv")
```

### Observe data

```{r}
names(publica)

max(publica$created_at)
min(publica$created_at)
```

Created_at is defined by: date ad was first collected by the Political Ad Collector
Updated_at is defined by: the most recent time that it got an impression OR the most recent time it was voted on

```{r}
publica %>% filter(created_at != updated_at) %>% select(created_at, updated_at)
```

political means: number of Political Ad Collector users who have voted that the ad is political
not_political means: number of Political Ad Collector users who have voted that the ad is not political

```{r}
publica %>% select(political) %>% count(political)
publica %>% select(not_political) %>% count(not_political)
```


```{r}
boxplot(publica$political)
hist(publica$political)
summary(publica$political)

boxplot(publica$not_political)
hist(publica$not_political)
summary(publica$not_political)
```


impression means: number of times the ad has been seen by the Political Ad Collector


```{r}
summary(publica$impressions)
boxplot(publica$impressions)
hist(publica$impressions)

```


political_probability means: calculated by the classifier. data only includes ads with a probability >=0.7

```{r}
summary(publica$political_probability)
boxplot(publica$political_probability)
hist(publica$political_probability)

publica %>% summarize(political_probability)
```


targeting: Facebook’s “Why am I seeing this?” disclosure provided to Political Ad Collector users

```{r}
publica %>% summarize(targeting)

publica[4,14]
```


targets: a parsed version of targeting

target has couple factors we need to decipher:
1. age which has two format, x and older and x to y. Need to put the formats in similar version. Can use dplyr to cut based on "and" and "to"
2. location: it has different formats like "region" which seem to refer to general location (can take many things like country, state, etc), "state" which refers to the state, "city" which refers to city
3. "Segment" and etc: takes in different sets of values like preference for the subject. ie: "NPR", "US politics (very liberal)", "Politics and social issues"

#### targets

```{r}
publica %>% summarize(targets)
publica %>% select(targets) %>% count(targets)

target_obs <- publica %>% select(targets) %>% count(targets)
target_obs

publica[4,16] 
```

```{r}
length(publica$targets)

sum(publica$targets == "[]")

sum(publica$targets == "[]")/length(publica$targets)

sum(publica$targets == "")

sum(publica$targets == "")/length(publica$targets)
```


advertiser: the account that posted the ad

```{r}
publica %>% summarize(advertiser)
```


entities: named entities mentioned in the ad, extracted using software
general info on the person and such

```{r}
publica %>% summarize(entities)
```

paid_for_by: for political ads, the entity listed in Facebook’s required disclosure as having paid for the ad 

```{r}
publica %>% select(paid_for_by) %>% count(paid_for_by)
```

targetedness: an internal metric for estimating how granularly an ad is targeted, used for sorting in the ProPublica search interface

```{r}
publica %>% select(targetedness) %>% count(targetedness)

summary(publica$targetedness)
hist(publica$targetedness)
boxplot(publica$targetedness)
```

```{r}
publica %>% select(listbuilding_fundraising_proba) %>% count(listbuilding_fundraising_proba)

summary(publica$listbuilding_fundraising_proba)
hist(publica$listbuilding_fundraising_proba)
boxplot(publica$listbuilding_fundraising_proba)
```


### DataExplorer

```{r}
introduce(publica)
plot_intro(publica)
plot_missing(publica)
```

```{r}
plot_bar(publica)
plot_histogram(publica)
```
```{r}
plot_qq(publica)
```

```{r}
plot_correlation(publica)
plot_correlation(na.omit(publica), maxcat = 5L)
```

## Load Data Advertise
```{r}
mono <- fread("/Users/paulhwang/Desktop/Distributed Computing/Project 2/Data/fb_monolith.csv")
```


Ad_id. Unique ID generated by Meta for this ad. (There may be multiple duplicate ads with the same content, but different ids.)
Page_name. Page name of the entity which published the ad.
Political_value. A number ranging from 0-1, populated by C4D’s political classification model. Ads that Meta indicates are political (because they have disclosures) have a value of -1, as C4D’s political classifier did not run on these ads.
Paid_for_by. Name of the entity listed in the ad disclosure. This field will be empty if the ad does not have a disclosure (that is, it’s not a declared political ad).
Ad_text. Text content of the ad.
Observed_at. Date/time when ad was observed.
Call_to_action. Text on button in ad, if there is one. (This might be donate, subscribe, etc.)
Targetings. Jsn object containing all of the targeting information collected for this ad. A description of the specific fields in this json object are shown below.


### Observe Data

```{r}
names(mono)
```

page_name

```{r}
mono %>% select(page_name) %>% count(page_name)
```

political_values: generally -1, but other values with min of 0.8

```{r}
mono %>% select(political_value) %>% count(political_value)

mono_political <- as.numeric(mono$political_value)
summary(mono_political)
boxplot(mono_political)
hist(mono_political)
```

paid_for_by: who paid to get the ad up

```{r}
mono %>% select(paid_for_by) %>% count(paid_for_by)
```

observed_at: Date/time when ad was observed.

```{r}
mono %>% select(observed_at) %>% count(observed_at)
```

Call_to_action. Text on button in ad, if there is one. (This might be donate, subscribe, etc.)

```{r}
mono %>% select(call_to_action) %>% count(call_to_action)
```



Targetings: Jsn object containing all of the targeting information collected for this ad. A description of the specific fields in this json object are shown below.

```{r}
mono %>% select(targetings) %>% count(targetings)

mono_targets <- mono %>% select(targetings)
```


### DateExplorer

```{r}
introduce(mono)
plot_intro(mono)
plot_missing(mono)
```

```{r}
str(mono)
```


## subset targets


```{r}
publica2 <- publica %>% filter(targets != "[]")
publica3 <- publica2 %>% filter(targets != "")

setwd("/Users/paulhwang/Desktop/Distributed Computing/Project 2/Data/")
fwrite(publica3, "propublica_cleantargets.csv")
```

```{r}
publica4 <- publica3 %>% sample_n(1000)
```

```{r}
fwrite(publica4, "propublica_1000.csv")
```


```{r}
test_pub <- fread("/Users/paulhwang/Desktop/Distributed Computing/Project 2/Data/propublica_cleantargets.csv")
```




```{r}
dim(test_pub)
```

```{r}
publica4 %>% select(targets) %>% count(targets)
```


```{r}
pro1000$message
```

## checking sentiment analysis

```{r}
tar_on <- fread("/Users/paulhwang/Desktop/Distributed Computing/Project 2/Data/propublica_sent.csv")
```

```{r}
hist(tar_on$avg_word_length)
hist(tar_on$word_count)
hist(tar_on$sentiment_score)
```


## Merging targets back propublica

```{r}
targets <- fread("/Users/paulhwang/Desktop/Distributed Computing/Project 2/Data/full_data_with_targets.csv")
```
```{r}
targets_test <- targets %>% select(id, target_Interest, target_Region, 
                                   target_City, target_Language, target_MaxAge, 
                                   target_Age, target_State, target_Retargeting, 
                                   target_Gender, target_Like, target_List, 
                                   target_Segment, target_MinAge, target_Agency, 
                                   target_Website)
```


```{r}
publica_merge <- left_join(tar_on, targets_test, by = "id")
```

```{r}
propublica_final <- publica_merge %>% 
  select(-html, -thumbnail, -images, -targeting, -suppressed, -targets, -page, 
         -lower_page, -targetings, -words)
```

```{r}
setwd("/Users/paulhwang/Desktop/Distributed Computing/Project 2/Data/")
fwrite(propublica_final, "propublica_final.csv")
```


```{r}
test = fread("/Users/paulhwang/Desktop/Distributed Computing/Project 2/Data/merged_data.csv")
```




## Data Viz Publica

```{r}
library(data.table)
library(dplyr)
library(ggplot2)
library(zoo)
library(lubridate)
```




```{r}
publica_final <- fread("/Users/paulhwang/Desktop/Distributed Computing/Project 2/Data/propublica_final.csv")
```

```{r}
publica_fin <- publica_final %>% mutate(date = as.Date(created_at), 
                         year = format(date, format = "%Y"), 
                         month = format(date, format = "%m"),
                         day = format(date, format = "%d"))

publica_fin
```

### Simple looks

```{r}
publica_fin %>% select(year, target_Gender) %>% count(target_Gender) ## yes
publica_fin %>% select(year, target_Age) %>% count(target_Age) ## not
publica_fin %>% select(year, target_MinAge) %>% count(target_MinAge) ## yes
publica_fin %>% select(year, target_MaxAge) %>% count(target_MaxAge) ## yes
publica_fin %>% select(year, target_Interest) %>% count(target_Interest) ## not
publica_fin %>% select(year, target_Region) %>% count(target_Region) ## sure...
publica_fin %>% select(year, target_State) %>% count(target_State) ## proof of crap
publica_fin %>% select(year, target_Language) %>% count(target_Language) ## enough
publica_fin %>% select(year, target_Retargeting) %>% count(target_Retargeting) ## sure
publica_fin %>% select(year, target_Agency) %>% count(target_Agency) ##no idea what this means
publica_fin %>% select(year, target_Website) %>% count(target_Website) ## useless

## completely empty
publica_fin %>% select(year, target_Like) %>% count(target_Like)
publica_fin %>% select(year, target_List) %>% count(target_List)
publica_fin %>% select(year, target_Segment) %>% count(target_Segment)
```

### breaking based on years


#### Gender
```{r}
df_gender <- publica_fin %>% select(year, target_Gender) %>% group_by(year) %>% 
  count(target_Gender) %>% mutate(prop = n/sum(n))

df_gender

ggplot(df_gender, aes(x = year, y = prop, fill = target_Gender)) + 
  geom_bar(stat = "identity", position = position_dodge()) + theme_classic() +
  labs(title = "Gender Targetting for Ads", x = "Year", y="Proportion") +
  coord_cartesian(ylim = c(0, 1.1), expand =FALSE)

df_gender_na <- publica_fin %>% select(year, target_Gender) %>% 
  filter(target_Gender != "") %>% group_by(year) %>% 
  count(target_Gender) %>% mutate(prop = n/sum(n))
df_gender_na


ggplot(df_gender_na, aes(x = year, y = prop, fill = target_Gender)) + 
  geom_bar(stat = "identity", position = position_dodge()) + theme_classic() +
  labs(title = "Gender Targetting for Ads", x = "Year", y="Proportion") +
  coord_cartesian(ylim = c(0, 0.9), expand =FALSE)
```

#### Age

```{r}
## overall -- doomsday

df_age <- publica_fin %>% select(date, target_MinAge, target_MaxAge)
df_age

ggplot(df_age, aes(x=date, y=target_MinAge)) + geom_line() + 
  scale_x_date(date_breaks = "1 month") + theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = -0.01))

## per day split

df_age_mean <- df_age %>% group_by(date) %>%
  summarize(mean_Min = mean(target_MinAge, na.rm = TRUE), 
            mean_Max = mean(target_MaxAge, na.rm = TRUE))

df_age_mean


ggplot(df_age_mean, aes(x = date, y = mean_Min)) +
  geom_line(aes(col = "Min Age")) +
  geom_line(aes(x = date, y = mean_Max, col = "Max Age")) +
  scale_x_date(date_breaks = "1 month") +
  scale_color_manual(values = c("blue", "red"), 
                     labels = c("Max Age", "Min Age")) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(title = "Target Age Range", x = "", y = "Age")
```

```{r}
merged_data$year_month <- paste(merged_data$year, month(merged_data$date), sep = "-")
merged_data$year_month <- ifelse(is.na(merged_data$date), NA, merged_data$year_month)
merged_data$year_month <- ifelse(nchar(merged_data$year_month) == 6, 
                                 paste0(merged_data$year, "-0",  month(merged_data$date)),
                                 merged_data$year_month)


df_ym <- publica_fin %>% select(date, year, month, target_MinAge, target_MaxAge)

df_ym <- publica_fin %>% 
  select(date, year, month, target_MinAge, target_MaxAge) %>%
  mutate(ym = paste(year, month, sep = "-")) %>%
  mutate(ym = ifelse(is.na(date), NA, ym)) %>%
  mutate(ym = as.Date(paste0(ym, "-01")))

df_ageym_mean <- df_ym %>% group_by(ym) %>%
  summarize(mean_Min = mean(target_MinAge, na.rm = TRUE), 
            mean_Max = mean(target_MaxAge, na.rm = TRUE))

df_ageym_mean


ggplot(df_ageym_mean, aes(x = ym, y = mean_Min)) +
  geom_line(aes(col = "Min Age")) +
  geom_line(aes(x = ym, y = mean_Max, col = "Max Age")) +
  scale_x_date(date_breaks = "1 month") +
  scale_color_manual(values = c("blue", "red"), 
                     labels = c("Max Age", "Min Age")) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(title = "Target Age Range, Averaged by Month", x = "", y = "Age")
```




#### Interest

```{r}
publica_fin %>% select(year, target_Interest) %>% count(target_Interest) %>% 
  mutate(prop = round(n/sum(n), digits = 3)) %>% filter(n > 400)
```

#### region

```{r}
publica_fin %>% select(year, target_Region) %>% count(target_Region) %>% 
  mutate(prop = round(n/sum(n), digits = 3)) %>% filter(n > 300)
```

#### state

```{r}
publica_fin %>% select(year, target_State) %>% count(target_State) %>% 
  mutate(prop = round(n/sum(n), digits = 3)) %>% filter(n > 100)
```

#### language


```{r}
publica_fin %>% select(year, target_Language) %>% count(target_Language) ## enough
publica_fin %>% select(year, target_Retargeting) %>% count(target_Retargeting) ## sure
publica_fin %>% select(year, target_Agency) %>% count(target_Agency) ##no idea what this means
publica_fin %>% select(year, target_Website) %>% count(target_Website) ## useless
```









